%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OXFORD THESIS TEMPLATE

% Use this template to produce a standard thesis that meets the Oxford University requirements for DPhil submission
%
% Originally by Keith A. Gillow (gillow@maths.ox.ac.uk), 1997
% Modified by Sam Evans (sam@samuelevansresearch.org), 2007
% Modified by John McManigle (john@oxfordechoes.com), 2015
% Modified by Ulrik Lyngs (ulrik.lyngs@cs.ox.ac.uk), 2018-, for use with R Markdown
%
% Ulrik Lyngs, 25 Nov 2018: Following John McManigle, broad permissions are granted to use, modify, and distribute this software
% as specified in the MIT License included in this distribution's LICENSE file.
%
% John commented this file extensively, so read through to see how to use the various options.  Remember that in LaTeX,
% any line starting with a % is NOT executed.

%%%%% PAGE LAYOUT
% The most common choices should be below.  You can also do other things, like replace "a4paper" with "letterpaper", etc.

% 'twoside' formats for two-sided binding (ie left and right pages have mirror margins; blank pages inserted where needed):
%\documentclass[a4paper,twoside]{templates/ociamthesis}
% Specifying nothing formats for one-sided binding (ie left margin > right margin; no extra blank pages):
%\documentclass[a4paper]{ociamthesis}
% 'nobind' formats for PDF output (ie equal margins, no extra blank pages):
%\documentclass[a4paper,nobind]{templates/ociamthesis}

% As you can see from the line below, oxforddown uses the a4paper size, 
% and passes in the binding option from the YAML header in index.Rmd:
\documentclass[a4paper, nobind]{templates/ociamthesis}


%%%%% ADDING LATEX PACKAGES
% add hyperref package with options from YAML %
\usepackage[pdfpagelabels]{hyperref}
% handle long urls
\usepackage{xurl}
% change the default coloring of links to something sensible
\usepackage{xcolor}

\definecolor{mylinkcolor}{RGB}{0,0,139}
\definecolor{myurlcolor}{RGB}{0,0,139}
\definecolor{mycitecolor}{RGB}{0,33,71}

\hypersetup{
  hidelinks,
  colorlinks,
  linktocpage=true,
  linkcolor=mylinkcolor,
  urlcolor=myurlcolor,
  citecolor=mycitecolor
}


% add float package to allow manual control of figure positioning %
\usepackage{float}

% enable strikethrough
\usepackage[normalem]{ulem}

% use soul package for correction highlighting
\usepackage{color, soulutf8}
\definecolor{correctioncolor}{HTML}{CCCCFF}
\sethlcolor{correctioncolor}
\newcommand{\ctext}[3][RGB]{%
  \begingroup
  \definecolor{hlcolor}{#1}{#2}\sethlcolor{hlcolor}%
  \hl{#3}%
  \endgroup
}
% stop soul from freaking out when it sees citation commands
\soulregister\ref7
\soulregister\cite7
\soulregister\citet7
\soulregister\autocite7
\soulregister\textcite7
\soulregister\pageref7

%%%%% FIXING / ADDING THINGS THAT'S SPECIAL TO R MARKDOWN'S USE OF LATEX TEMPLATES
% pandoc puts lists in 'tightlist' command when no space between bullet points in Rmd file,
% so we add this command to the template
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 
% allow us to include code blocks in shaded environments

% User-included things with header_includes or in_header will appear here
% kableExtra packages will appear here if you use library(kableExtra)
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}


%UL set section header spacing
\usepackage{titlesec}
% 
\titlespacing\subsubsection{0pt}{24pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}


%UL set whitespace around verbatim environments
\usepackage{etoolbox}
\makeatletter
\preto{\@verbatim}{\topsep=0pt \partopsep=0pt }
\makeatother


%%%%%%% PAGE HEADERS AND FOOTERS %%%%%%%%%
\usepackage{fancyhdr}
\setlength{\headheight}{15pt}
\fancyhf{} % clear the header and footers
\pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{\thechapter. #1}{\thechapter. #1}}
\renewcommand{\sectionmark}[1]{\markright{\thesection. #1}} 
\renewcommand{\headrulewidth}{0pt}





% UL page number position 
\fancyfoot[C]{\emph{\thepage}} %regular pages
\fancypagestyle{plain}{\fancyhf{}\fancyfoot[C]{\emph{\thepage}}} %chapter pages




%%%%% SELECT YOUR DRAFT OPTIONS
% This adds a "DRAFT" footer to every normal page.  (The first page of each chapter is not a "normal" page.)

% IP feb 2021: option to include line numbers in PDF

% for line wrapping in code blocks
\usepackage{fancyvrb}
\usepackage{fvextra}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines=true, breakanywhere=true, commandchars=\\\{\}}

% This highlights (in blue) corrections marked with (for words) \mccorrect{blah} or (for whole
% paragraphs) \begin{mccorrection} . . . \end{mccorrection}.  This can be useful for sending a PDF of
% your corrected thesis to your examiners for review.  Turn it off, and the blue disappears.


%%%%% BIBLIOGRAPHY SETUP
% Note that your bibliography will require some tweaking depending on your department, preferred format, etc.
% If you've not used LaTeX before, I recommend just using pandoc for citations -- this is what's used unless you specific e.g. "citation_package: natbib" in index.Rmd
% If you're already a LaTeX pro and are used to natbib or something, modify as necessary.

% this allows the latex template to handle pandoc citations




% Uncomment this if you want equation numbers per section (2.3.12), instead of per chapter (2.18):
%\numberwithin{equation}{subsection}


%%%%% THESIS / TITLE PAGE INFORMATION
% Everybody needs to complete the following:




% Master's candidates who require the alternate title page (with candidate number and word count)
% must also un-comment and complete the following three lines:

% Uncomment the following line if your degree also includes exams (eg most masters):
%\renewcommand{\submittedtext}{Submitted in partial completion of the}
% Your full degree name.  (But remember that DPhils aren't "in" anything.  They're just DPhils.)


% Term and year of submission, or date if your board requires (eg most masters)



%%%%% YOUR OWN PERSONAL MACROS
% This is a good place to dump your own LaTeX macros as they come up.

% To make text superscripts shortcuts
\renewcommand{\th}{\textsuperscript{th}} % ex: I won 4\th place
\newcommand{\nd}{\textsuperscript{nd}}
\renewcommand{\st}{\textsuperscript{st}}
\newcommand{\rd}{\textsuperscript{rd}}

%%%%% THE ACTUAL DOCUMENT STARTS HERE
\begin{document}

%%%%% CHOOSE YOUR LINE SPACING HERE
% This is the official option.  Use it for your submission copy and library copy:
\setlength{\textbaselineskip}{22pt plus2pt}
% This is closer spacing (about 1.5-spaced) that you might prefer for your personal copies:
%\setlength{\textbaselineskip}{18pt plus2pt minus1pt}

% You can set the spacing here for the roman-numbered pages (acknowledgements, table of contents, etc.)
\setlength{\frontmatterbaselineskip}{17pt plus1pt minus1pt}

% UL: You can set the line and paragraph spacing here for the separate abstract page to be handed in to Examination schools
\setlength{\abstractseparatelineskip}{13pt plus1pt minus1pt}
\setlength{\abstractseparateparskip}{0pt plus 1pt}

% UL: You can set the general paragraph spacing here - I've set it to 2pt (was 0) so
% it's less claustrophobic
\setlength{\parskip}{2pt plus 1pt}

%
% Customise title page
%
\def\crest{}
\renewcommand{\university}{}
\renewcommand{\submittedtext}{}
\renewcommand{\thesistitlesize}{\fontsize{22pt}{28pt}\selectfont}
\renewcommand{\gapbeforecrest}{25mm}
\renewcommand{\gapaftercrest}{25mm
}


% Leave this line alone; it gets things started for the real document.
\setlength{\baselineskip}{\textbaselineskip}


%%%%% CHOOSE YOUR SECTION NUMBERING DEPTH HERE
% You have two choices.  First, how far down are sections numbered?  (Below that, they're named but
% don't get numbers.)  Second, what level of section appears in the table of contents?  These don't have
% to match: you can have numbered sections that don't show up in the ToC, or unnumbered sections that
% do.  Throughout, 0 = chapter; 1 = section; 2 = subsection; 3 = subsubsection, 4 = paragraph...

% The level that gets a number:
\setcounter{secnumdepth}{2}
% The level that shows up in the ToC:
\setcounter{tocdepth}{1}


%%%%% ABSTRACT SEPARATE
% This is used to create the separate, one-page abstract that you are required to hand into the Exam
% Schools.  You can comment it out to generate a PDF for printing or whatnot.

% JEM: Pages are roman numbered from here, though page numbers are invisible until ToC.  This is in
% keeping with most typesetting conventions.
\begin{romanpages}

% Title page is created here

%%%%% DEDICATION

%%%%% ACKNOWLEDGEMENTS


%%%%% ABSTRACT


%%%%% MINI TABLES
% This lays the groundwork for per-chapter, mini tables of contents.  Comment the following line
% (and remove \minitoc from the chapter files) if you don't want this.  Un-comment either of the
% next two lines if you want a per-chapter list of figures or tables.
\dominitoc % include a mini table of contents

% This aligns the bottom of the text of each page.  It generally makes things look better.
\flushbottom

% This is where the whole-document ToC appears:


% Uncomment to generate a list of tables:
%%%%% LIST OF ABBREVIATIONS
% This example includes a list of abbreviations.  Look at text/abbreviations.tex to see how that file is
% formatted.  The template can handle any kind of list though, so this might be a good place for a
% glossary, etc.

% The Roman pages, like the Roman Empire, must come to its inevitable close.
\end{romanpages}

%%%%% CHAPTERS
% Add or remove any chapters you'd like here, by file name (excluding '.tex'):
\flushbottom

% all your chapters and appendices will appear here
\hypertarget{introduction}{%
\chapter{Introduction}\label{introduction}}

This dissertation aims to broaden our understanding of gastropopulism to accommodate a range of ideological and regional contexts. The emerging research on gastropopulism explores it in conflation with right-wing discursive ideology, specifically exclusionary nationalism. Furthermore, the empirical evidence heavily relies (70\%) on the content of a single actor, which distorts the findings. These factors are forming a vicious circle, entrenching a limited and biased understanding of gastropopulism. The political implication of academic conflation of (gastro)populism with nationalism is the validation of harmful claims as `soft' and representative of ``the people'' (Hunger and Paxton, 2021, p630). As such, there is a significant gap in the literature that necessitates radical review of gastropopulism. In this dissertation I have designed and applied a research methodology to overcome the current divides in populism research: conflation with ideology; insensitivity to geographical/cultural contexts; differences between quantitative and qualitative methods (Hunger and Paxton, 2021, p629).

Research Question: \textbf{\emph{How do political actors use multimodal gastropopulist performances to construct and legitimise their public identities?}}

In this dissertation, `multimodal communication', `gastropopulism', and `public identities' are divided into the following elements. Multimodal communication integrates the individual communicative modes of language, food and the body (Norris, 2004, p152). The features of gastropopulist performances are (1) belonging with `the people'; (2) bad manners; (3) immediacy (Moffitt, 2016, p40). A public identity is constructed through emphasising selected roles, herein, celebrity, politician, personal, and professional (Bast, 2021, p200).

Accordingly, my account formulates gastropopulism as \emph{an actor's use of multimodal communication integrating language, food, and the body in performances of connecting with `the people', bad manners, and immediacy, in order to construct a consistent public identity that performs authenticity through strategically blending their celebrity, politician, personal, and professional roles}.

To test my account, I have undertaken mixed-methods analysis of visual and audiovisual data of Alexandria Ocasio-Cortez \{{[}AOC{]}\} (left-wing, US), Donald Trump (right-wing, US), Nigel Farage (right-wing, UK) and Jeremy Corbyn (left-wing, UK). My research design is complex but comprehensive and cohesive, structured as follows. \textbf{Chapter Two: Integrative Literature Review} offers a qualitative synthesis of the relevant themes to the emerging field of gastropopulism, namely: populism; performance and multimodal communication; celebrity and social media; food semiotics and the body. I then critically assess the three existing empirical studies of gastropopulism to clearly establish the gap in the literature and the need to challenge and extend our knowledge of gastropopulism. \textbf{Chapter Three: Multimodal Social Semiotics Research Approach} outlines my methodological considerations, sample, and methods. This presents descriptive statistics for my sample. My methods and coding process are discussed, and my codebook for gastropopulist features is presented. \textbf{Chapter Four: Statistical Analysis} generates summary statistics of key variables for my entire sample {[}n=163{]}, by actor, ideology, region, and overall, to examine how gastropopulist performances are constructed. This chapter demonstrates why empirical evidence of gastropopulism is suited to analytic, not statistical, generalisability. Furthermore, the empirical grounding of the subsequent chapters is established. \textbf{Chapter Five: Individual Timeline Thematic Analysis} is a mixed-methods examination of each actor's data, using quantitative interactive timeline visualisations paired with qualitative discussions of individual trends, generated through inductive thematic analysis. This examines how the actors demonstrate their belonging to their people: Trump uses his personal wealth to buy his people fast food; AOC physically belongs in her constituency; Corbyn uses his campaign slogan `For The Many'; Farage uses food/drink to represent the cause/solution of problems. \textbf{Chapter Six: Nationalism and Class} uses deductive qualitative thematic analysis to explore how the central themes of extant gastropopulism literature manifest in my sample and theory. The `nationalism' section critically assesses the exclusionary/inclusionary binary presented by the literature, as well as the conflation of gastropopulism with right-wing discursive ideology. The `class' section considers how the actors embody class solidarity through performing a pub/bar worker role, apart from Trump, who integrates his professional identity into his food choices. This chapter dissects what it means for a gastropopulist performance to be viewed as credible. \textbf{Chapter Seven: Performative Eating} analyses performative eating videos using an original framework, Multimodal Social Semiotics Timeline Transcription. This explores the unique affordances of turning eating into a spectacle for gastropopulist performers. \textbf{Chapter Eight: Discussion} reflects upon the theory and arguments brought forth. This considers the work's limitations and offers opportunities for future research. Ultimately, I conclude that
political actors use multimodal gastropopulist performances as an effective impression management strategy to construct and legitimise their public identities. Furthermore, I defend my position that disentangling gastropopulism from ideological assumptions is necessary and achievable; my research design facilitates a comprehensive understanding of gastropopulism \emph{qua} gastropopulism that can comfortably accommodate different ideological and regional contexts.

%%%%% REFERENCES


\end{document}
